---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  warning = FALSE
)
```

```{r load_main, include = FALSE}
#downloads from the documentation project
url <- "https://raw.githubusercontent.com/Covid19R/documentation/master/onboarding.Rmd"
download.file(url, "tmp.Rmd")

```

```{r import-main, child = 'tmp.Rmd'}
```

```{r unlink, include = FALSE}
unlink("tmp.Rmd")
```

-----------

# covid19tunisia

<!-- badges: start -->
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-orange.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![CRAN status](https://www.r-pkg.org/badges/version/YOUR_PACKAGE)](https://CRAN.R-project.org/package=covid19tunisia)
[![Travis build status](https://travis-ci.org/Covid19R/covid19tunisia.svg?branch=master)](https://travis-ci.org/USER_OR_ORG/covid19tunisia)
<!-- badges: end -->

The  covid19tunisia package harvests the data made freely available by [Mouna Belaid](https://github.com/MounaBelaid/covid19datatunisia).

## Installation

ONLY INCLUDE IF SUBMITTED TO/ON CRAN You can install the released version of covid19nytimes from [CRAN](https://CRAN.R-project.org) with:

``` {r install, eval=FALSE}
install.packages("covid19tunisia")
```

Or the latest development version from [github](https://github.com/USER_OR_ORG/covid19tunisia)

```{r install_github, eval = FALSE}
devtools::install_github("USER_OR_ORG/covid19tunisia")
```
## Data

```{r example}
library(covid19tunisia)
```

Get the full dataset:

```{r}
(france <- refresh_covid19tunisia())
```

To switch to a wider format, you can use `tidyr`:

```{r}
france %>% 
  tidyr::pivot_wider(
    names_from = "data_type"
  ) %>% 
  dplyr::select(
    1, 6:ncol(.), everything()
  )
```

For more info on the dataset:

```{r}
get_info_covid19tunisia()
```

## Columns

The data follows the [covid19R standard for tidy Covid-19 data](https://covid19r.github.io/documentation/data-format-standard.html). The data columns are as follows:

● date - The date in YYYY-MM-DD form.

● location - The name of the government as provided by the data sources.

● location_type - The type of location using the covid19R controlled vocabulary. In this case, it's “state_government”.

● location_code - A standardized location code using a national or international standard. In this case, . See https://www.iso.org/obp/ui/#iso:code:3166:TN for details.

● location_code_type The type of standardized location code being used according to the covid19R controlled vocabulary. Here we use “ISO 3166-2:TN”.

● data_type - the type of data in that given row. Includes cases new : new confirmed Covid-19 cases during on the current date, recovered_new : new number of patients recovered on the current date and deaths_new : new deaths on the current datea.

● value - number of cases of each data type.

## Contributing

Please submit [issues](https://github.com/Covid19R/covid19tunisia/issues) and [pull requests](https://github.com/Covid19R/covid19tunisia/pulls) with any package improvements!

Please note that the 'covid19tunisia' project is released with a
[Contributor Code of Conduct](https://github.com/Covid19R/covid19tunisia/blob/master/CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.

