---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

```{r load_main, include = FALSE}
#downloads from the documentation project
url <- "https://raw.githubusercontent.com/Covid19R/documentation/master/onboarding.Rmd"
download.file(url, "tmp.Rmd")

```

```{r import-main, child = 'tmp.Rmd'}
```

```{r unlink, include = FALSE}
unlink("tmp.Rmd")
```

-----------

# YOUR_PACKAGE_NAME

<!-- badges: start -->
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-orange.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![CRAN status](https://www.r-pkg.org/badges/version/YOUR_PACKAGE)](https://CRAN.R-project.org/package=YOUR_PACKAGE)
[![Travis build status](https://travis-ci.org/Covid19R/YOUR_PACKAGE.svg?branch=master)](https://travis-ci.org/USER_OR_ORG/YOUR_PACKAGE)
<!-- badges: end -->

The  YOUR_PACKAGE package harvests the data made freely available by the XXX. See USEFUL_URL_ABOUT_DATA for more.

## Installation

ONLY INCLUDE IF SUBMITTED TO/ON CRAN You can install the released version of covid19nytimes from [CRAN](https://CRAN.R-project.org) with:

``` {r install, eval=FALSE}
install.packages("YOUR_PACKAGE")
```

Or the latest development version from [github](https://github.com/USER_OR_ORG/YOUR_PACKAGE)

```{r install_github, eval = FALSE}
devtools::install_github("USER_OR_ORG/YOUR_PACKAGE")
```

## Data

The package has the data from XXXXXX. The package comes with static data that was downloaded at the time of the last package update.

```{r head_of_data, eval = FALSE}
library(YOUR_LIBRARY_NAME)

head(DATA) %>% knitr::kable()

```

## Getting the Most Up to Date Data

To get the most updated data, run the following functions

```{r refresh}
```

## Columns

The data follows the [covid19R standard for tidy Covid-19 data](https://covid19r.github.io/documentation/data-format-standard.html). The data columns are as follows:

* date - The date in YYYY-MM-DD form
* location - The name of the location as provided by the data source. Nested locations are combined and separated by a `,`, and can be split by `tidyr::separate()`, if you wish.
* location_type - The type of location using the [Covid19R Controlled Vocabulary](https://covid19r.github.io/documentation/standardized-vocabulary.html). Nested locations are indicated by multiple location types being combined with a `_`
* location_code - A standardized location code using a national or international standard. MORE HERE
* location_code_type The type of standardized location code being used according to the covid19R controlled vocabulary. Here we use `XXX`
* data_type - the type of data in that given row from the [Covid19R Controlled Vocabulary](https://covid19r.github.io/documentation/standardized-vocabulary.html). What is here?
* value - number of cases of each data type
* OTHER COLUMNS - WHAT THEY MEAN

## Sample visualization

```{r example_plot}
```
