---
title: "Introduction to the covid19tunisia package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{intro}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The covid19tunisia R package provides a tidy format dataset of the 2019 Novel Coronavirus COVID-19 (2019-nCoV) pandemic outbreak in Tunisia. The package 
covers a daily summary of the outbreak on the national level.

The data was pull from :

- [Official Facebook page of the Tunisian Ministry of Health](https://tinyurl.com/y7uvomew) through their daily published press releases.

- [National Observatory of New and Emerging Diseases](http://www.onmne.tn/fr/publications.php?id_rub=5&id=123)

- Regional governments in Tunisia.

## Installation

You can install the released version of covid19tunisia from [CRAN](https://cran.r-project.org/package=covid19tunisia) with:

``` r
install.packages("covid19tunisia")
```

## Overview

The `covid19tunisia` dataset provides an overall summary of the cases in Tunisia since the beginning of the covid19 outbreak on 
March 2, 2020. The dataset contains the following fields:

▲ `date` - The date in YYYY-MM-DD form.

▲ `location` - The name of the government as provided by the data sources.

▲ `location_type` - The type of location using the covid19R controlled vocabulary. In this case, it's “state”.

▲ `location_code` - A standardized location code using a national or international standard. In this case, . See https://www.iso.org/obp/ui/#iso:code:3166:TN for details.

▲ `location_code_type` The type of standardized location code being used according to the covid19R controlled vocabulary. Here we use “ISO 3166-2”.

▲ `data_type` - the type of data in that given row. Includes cases new : new confirmed Covid-19 cases during on the current date,
recovered_new : new number of patients recovered on the current date and deaths_new : new deaths on the current date.

▲ `value` - number of cases of each data type.

```{r}
library(covid19tunisia)

data <- refresh_covid19tunisia()

head(data)

str(data)

```

### Plotting the daily evolution of active cases

``` r
# Transform the data

library(dplyr)
library(tidyr)
library(plotly)

data_transformed <- data %>% group_by(date,data_type) %>% summarise(value=sum(value)) %>% 
                    spread(data_type,value)

head(data_transformed)
# A tibble: 6 x 4
# Groups:   date [6]
  date       cases_new deaths_new recovered_new
  <date>         <dbl>      <dbl>         <dbl>
1 2020-03-02         1          0             0
2 2020-03-08         1          0             0
3 2020-03-09         3          0             0
4 2020-03-10         1          0             0
5 2020-03-11         1          0             0
6 2020-03-12         6          0             0

  data_transformed %>%
  ungroup() %>% plot_ly(type = 'scatter', 
                        mode = 'lines+markers')%>% 
  add_trace(x = ~date, y = ~cumsum(cases_new), 
            name = 'Confirmed cases',
            marker = list(color = '#fec44f'),
            line = list(color = '#fec44f'),
            hoverinfo = "text",
            text = ~paste(cases_new, "New confirmed cases\n",cumsum(cases_new), 'Total number of infected cases on',date)) %>%
  add_trace(x = ~date, y = ~cumsum(deaths_new),
            name = 'Deaths',
            marker = list(color = 'red'),
            line = list(color = 'red'),
            hoverinfo = "text",
            text = ~paste(deaths_new, "New deaths\n",cumsum(deaths_new), 'Total number of deaths on',date)) %>%
  add_trace(x = ~date, y = ~cumsum(recovered_new), 
            name = 'Recovered cases',
            marker = list(color = 'green'),
            line = list(color = 'green'),
            hoverinfo = "text",
            text = ~paste(recovered_new, "New recovered cases\n",cumsum(recovered_new), 'Total number of recovered cases on',date)) %>% 
  layout(title = 'Tunisia - Daily Evolution of Active COVID19 Cases',
         legend = list(x = 0.1, y = 0.9,
                       font = list(family = "sans-serif", size = 14, color = "#000"), bgcolor = "",
                       bordercolor = "#FFFFFF", borderwidth = 2),
         xaxis = list(title = ""),
         yaxis = list(side = 'left', title = 'Daily evolution', showgrid = TRUE, zeroline = TRUE))
                        
```
